---
title: "adjusting_condition_file"
format: html
editor: visual
jupyter: python3
---

This file is organized by replacing the original .ses.con files with the 'master' .ses.con files that were manually created. We can substitute by scene or by category and can do either the pics or the vids depending on which one you are going through at the moment.

# Packages

```{r setup}
library(dplyr)
```

# Pick folder based on current computer

```{r}
# Andrew's last know location of data in sabat lab
sabat_data_folder <- "/Volumes/startech3TB_bkup/research_data/Pic_Vid"
andrew_data_folder <- "/home/andrewf/Research_data/EEG/Pic_Vid"

if (dir.exists(sabat_data_folder)) {
  parent_directory <- sabat_data_folder
  raw_data_folder <- paste0(sabat_data_folder, "/raw_data")
} else if(dir.exists(andrew_data_folder)) {
  parent_directory <- andrew_data_folder
  raw_data_folder <- paste0(andrew_data_folder, "/raw_data")
} else{
  stop("Something is wrong, are you working on the right computer with access to the data")
}

```

# Replacing all ses.con files.

```{r}
all_ses_cons <- list.files(raw_data_folder,
                           pattern = ".ses.con$",
                           recursive = T, 
                           full.names = T)

A_1_cons <- all_ses_cons[grepl(pattern = "A_1", x = all_ses_cons)]
A_2_cons <- all_ses_cons[grepl(pattern = "A_2", x = all_ses_cons)]
B_1_cons <- all_ses_cons[grepl(pattern = "B_1", x = all_ses_cons)]
B_2_cons <- all_ses_cons[grepl(pattern = "B_2", x = all_ses_cons)]
C_1_cons <- all_ses_cons[grepl(pattern = "C_1", x = all_ses_cons)]
C_2_cons <- all_ses_cons[grepl(pattern = "C_2", x = all_ses_cons)]
D_1_cons <- all_ses_cons[grepl(pattern = "D_1", x = all_ses_cons)]
D_2_cons <- all_ses_cons[grepl(pattern = "D_2", x = all_ses_cons)]
```

## For Videos

```{r}
file.copy(from = paste0(parent_directory, "/condition_files/by_scene/Condition_A_1.f.ses.con"),
          to = A_1_cons,
          overwrite = T)

file.copy(from = paste0(parent_directory, "/condition_files/by_scene/Condition_B_2.f.ses.con"),
          to = B_2_cons,
          overwrite = T)

file.copy(from = paste0(parent_directory, "/condition_files/by_scene/Condition_C_1.f.ses.con"),
          to = C_1_cons,
          overwrite = T)

file.copy(from = paste0(parent_directory, "/condition_files/by_scene/Condition_D_2.f.ses.con"),
          to = D_2_cons,
          overwrite = T)
```

## For Pictures

```{r}
file.copy(from = paste0(parent_directory, "/condition_files/by_scene/Condition_A_2.f.ses.con"),
          to = A_2_cons,
          overwrite = T)

file.copy(from = paste0(parent_directory, "/condition_files/by_scene/Condition_B_1.f.ses.con"),
          to = B_1_cons,
          overwrite = T)

file.copy(from = paste0(parent_directory, "/condition_files/by_scene/Condition_C_2.f.ses.con"),
          to = C_2_cons,
          overwrite = T)

file.copy(from = paste0(parent_directory, "/condition_files/by_scene/Condition_D_1.f.ses.con"),
          to = D_1_cons,
          overwrite = T)
```

# Replacing all of the ses.con files by category

```{r}

all_ses_cons <- list.files(raw_data_folder,
                           pattern = ".ses.con$",
                           recursive = T, 
                           full.names = T)

A_1_cons <- all_ses_cons[grepl(pattern = "A_1", x = all_ses_cons)]
A_2_cons <- all_ses_cons[grepl(pattern = "A_2", x = all_ses_cons)]
B_1_cons <- all_ses_cons[grepl(pattern = "B_1", x = all_ses_cons)]
B_2_cons <- all_ses_cons[grepl(pattern = "B_2", x = all_ses_cons)]
C_1_cons <- all_ses_cons[grepl(pattern = "C_1", x = all_ses_cons)]
C_2_cons <- all_ses_cons[grepl(pattern = "C_2", x = all_ses_cons)]
D_1_cons <- all_ses_cons[grepl(pattern = "D_1", x = all_ses_cons)]
D_2_cons <- all_ses_cons[grepl(pattern = "D_2", x = all_ses_cons)]
```

## For Vids

```{r}
file.copy(from = paste0(parent_directory, "/condition_files/by_category/Condition_A_1.f.ses.con"),
          to = A_1_cons,
          overwrite = T)

file.copy(from = paste0(parent_directory, "/condition_files/by_category/Condition_B_2.f.ses.con"),
          to = B_2_cons,
          overwrite = T)

file.copy(from = paste0(parent_directory, "/condition_files/by_category/Condition_C_1.f.ses.con"),
          to = C_1_cons,
          overwrite = T)

file.copy(from = paste0(parent_directory, "/condition_files/by_category/Condition_D_2.f.ses.con"),
          to = D_2_cons,
          overwrite = T)


```

## For Pics

```{r}
file.copy(from = paste0(parent_directory, "/condition_files/by_category/Condition_A_2.f.ses.con"),
          to = A_2_cons,
          overwrite = T)

file.copy(from = paste0(parent_directory, "/condition_files/by_category/Condition_B_1.f.ses.con"),
          to = B_1_cons,
          overwrite = T)

file.copy(from = paste0(parent_directory, "/condition_files/by_category/Condition_C_2.f.ses.con"),
          to = C_2_cons,
          overwrite = T)

file.copy(from = paste0(parent_directory, "/condition_files/by_category/Condition_D_1.f.ses.con"),
          to = D_1_cons,
          overwrite = T)
```
